Analysis

### 2023-03-28 Analysis.rmd
update table formatting

  df |>
    summarise_scores(by = c("model", "target_type", "scale", "horizon")) |>
    select(model, target_type, scale, interval_score, coverage_50, coverage_90, horizon) |>
    inner_join(sd) |>
    group_by(target_type, scale) |>
    mutate(relative = interval_score / interval_score[model == "EuroCOVIDhub-ensemble"]) |>
    mutate(across(c(where(is.numeric)), \(x) signif(x, digits = 2))) |>
    mutate(across(c(where(is.numeric)), \(x) label_fn(x))) |> 
    # mutate(interval_score = paste0(interval_score, " (", relative, "), sd: ", wis_sd)) |>
    # select(-relative, -wis_sd) |>
    pivot_wider(names_from = scale, values_from = c(interval_score, wis_sd, relative)) |>
    mutate(model = factor(model, levels = levels(models_non_human))) |>
    arrange(target_type, model) |>
    select(model, target_type, 
           interval_score_natural, relative_natural, wis_sd_natural, 
           interval_score_log, relative_log, wis_sd_log, 
           coverage_50, coverage_90) |>
    kable(format = "latex", booktabs = TRUE, 
          align = c("l", "l", rep("c", 4)),
          caption = cap,
          linesep = c('', '', '', '\\addlinespace'),
          col.names = c("Model", "Target", "abs.", "rel.", "sd", "abs.", "rel.", "sd", 
                        "Coverage 50%", "Coverage 90%")) |> 
    kable_styling(latex_options = c("scale_down", 
                                    "hold_position")) |>
    add_header_above(c(" " = 2, "WIS - natural" = 3, "WIS - log scale" = 3, " " = 2)) 
}

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(
    cap = "Performance for two-week-ahead forecasts. Standard deviations are given in brackets. \\label{tab:scores}"
    ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table.tex')

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(
    hor = 4, 
    cap = "Performance for four-week-ahead forecasts. Standard deviations are given in brackets. \\label{tab:scores-4}"
  ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-horizon-4.tex')
```

>>>>

  df |>
    summarise_scores(by = c("model", "target_type", "scale", "horizon")) |>
    select(model, target_type, scale, interval_score, coverage_50, coverage_90, horizon) |>
    inner_join(sd) |>
    group_by(target_type, scale) |>
    mutate(relative = interval_score / interval_score[model == "EuroCOVIDhub-ensemble"]) |>
    mutate(across(c(where(is.numeric)), \(x) round(signif(x, digits = 3), digits = 2))) |>
    mutate(across(c(where(is.numeric)), \(x) label_fn(x))) |> 
    # mutate(interval_score = paste0(interval_score, " (", relative, "), sd: ", wis_sd)) |>
    # select(-relative, -wis_sd) |>
    pivot_wider(names_from = scale, values_from = c(interval_score, wis_sd, relative)) |>
    mutate(model = factor(model, levels = levels(models_non_human))) |>
    arrange(target_type, model) |>
    select(model, target_type, 
           interval_score_natural, relative_natural, wis_sd_natural, 
           interval_score_log, relative_log, wis_sd_log, 
           coverage_50, coverage_90) |>
    kable(format = "latex", booktabs = TRUE, 
          align = c("l", "l", rep("c", 4)),
          caption = cap,
          linesep = c('', '', '', '\\addlinespace'),
          col.names = c("Model", "Target", "abs.", "rel.", "sd", "abs.", "rel.", "sd", 
                        "Coverage 50%", "Coverage 90%")) |> 
    kable_styling(latex_options = c("scale_down", 
                                    "hold_position")) |>
    add_header_above(c(" " = 2, "WIS - natural" = 3, "WIS - log scale" = 3, " " = 2)) 
}

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(
    cap = "Performance for two-week-ahead forecasts. Vallues have been cut to three significant digits and rounded.  \\label{tab:scores}"
    ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table.tex')

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(
    hor = 4, 
    cap = "Performance for four-week-ahead forecasts. Vallues have been cut to three significant digits and rounded \\label{tab:scores-4}"
  ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-horizon-4.tex')
```
